%%%%%%%%%%%%%%%%%%%% Document setup %%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
% Clear all header and footer fields
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
% Ensure that generate pdf is machine readable / ATS parsable
\pdfgentounicode=1


%%%%%%%%%%%%%%%%%%%% Commands %%%%%%%%%%%%%%%%%%%%
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-3pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}


%%%%%%%%%%%%%%%%%%%% Heading %%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
  {\Huge\scshape Phuc Gia Doan (Larry) Huynh}\\
  \vspace{3pt}
  \small{
    \href{https://www.larryhuynh.dev}{\raisebox{-0.2\height}\faGlobe\ \underline{larryhuynh.dev}}  ~
    \href{https://www.linkedin.com/in/larryhuynhdev}{\raisebox{-0.2\height}\faLinkedin\ \underline{larryhuynhdev}}  ~
    \href{https://github.com/larryh12}{\raisebox{-0.2\height}\faGithub\ \underline{larryh12}} ~
    \href{mailto:larryhuynh+work@protonmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{larryhuynh+work@protonmail.com}} ~
    \href{tel:+61414180258}{\raisebox{-0.2\height}\faPhone\  \underline{+61 414 180 258}}}
\end{center}
\vspace{-7pt}


%%%%%%%%%%%%%%%%%%%% About %%%%%%%%%%%%%%%%%%%%
\section{About}
  \small{High-achieving ICT graduate passionate about technology, excelling in solving complex problems with software engineering principles and data-driven strategies. My academic and professional experiences have honed my expertise in software engineering, data analytics, and project management. Driven to embrace new challenges, I continually refine my problem-solving abilities and thrive in collaborative, cross-functional teams. As a dedicated team player, I seek opportunities to leverage my skills and knowledge in developing technology solutions that drive business impact and contribute to core business values.}


%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Griffith University}{Brisbane, Queensland, Australia}
    {Bachelor of Information Technology, 6.8/7.0 GPA}{Mar 2019 -- Dec 2022}
        \resumeItemListStart
            \resumeItem{Recipient of the Griffith Academic Excellence Awards in 2019, 2020, and 2022.}
            \resumeItem{Awarded the Griffith School of ICT Award for Highest GPA Graduate in 2022.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Centre for Applied Energy Economics and Policy Research}{Brisbane, Queensland, Australia}
            {Software Engineer (Work-Integrated Learning)}{Jul 2022 -- Nov 2022}
            \resumeItemListStart
                \resumeItem{Developed a data pipeline application to analyse data from the Australian Energy Market Operator.}
                \resumeItem{Led cross-functional collaboration, managed application source code, and developed core features.}
		\resumeItem{Achieved an 80\% improvement in pipeline processing time and a 96\% increase in data extraction accuracy.}
		\resumeItem{Nominated for the 2022 FirstWave Awards in the ``Best Innovative Project'' category.}
		\resumeItem{\textbf{Skills:} Data Analysis, Python Programming, GitHub, Version Control, Technical Documentation, Project Management, Software Development Life Cycle (SDLC), Agile Methodologies.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%
\section{Projects} 
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {Breadit - Modern Full-Stack Reddit Clone}
        {\href{https://github.com/larryh12/breadit}{\underline{GitHub}}}
        \resumeItemListStart
            \resumeItem{Developed a full-stack, Reddit-based social platform application using Next.js and TypeScript.}
	    \resumeItem{Integrated user management with Clerk and a MySQL database via PlanetScale for subreddit, post, and user data.}
	    \resumeItem{Implemented object-relational schema mapping with Prisma, along with data caching using Upstash Redis.}
	    \resumeItem{Implemented client-side data fetching and validation utilising React Query and Zod.}
	    \resumeItem{Developed back-end APIs to leverage server-side rendering, serverless architecture, and Vercel’s Edge Functions.}
        \resumeItemListEnd
        \resumeProjectHeading
        {ChatGPT Free - Full-Stack ChatGPT Web Application}
        {\href{https://github.com/larryh12/chatgpt-free}{\underline{GitHub}}}
        \resumeItemListStart
            \resumeItem{Developed a free ChatGPT web application for geo-restricted regions, using Next.js and TypeScript.}
	    \resumeItem{Integrated user authentication with NextAuth and a NoSQL database with Firebase for user and conversation data.}
	    \resumeItem{Implemented GPT-3.5-Turbo text generation models using OpenAI’s Chat Completions API.}
	    \resumeItem{Implemented real-time conversation (live chat) in a serverless environment using Google Cloud Firestore.}
	    \resumeItem{Developed a front-end UI with a multi-theme switcher using Tailwind CSS and DaisyUI.}
        \resumeItemListEnd
        \resumeProjectHeading
        {FLIXX - Trending Movies, TV Shows, Anime Info}
        {\href{https://github.com/larryh12/flixx-app}{\underline{GitHub}}}
        \resumeItemListStart
            \resumeItem{Developed a website featuring trending movies, TV shows, and anime using vanilla HTML, CSS, and JavaScript.}
	    \resumeItem{Developed RESTful data fetching and parsing functions for the TMDB and MyAnimeList APIs.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%
\section{Skills}
    \begin{itemize}
    [leftmargin=0in, label={}]\small{\item{
        \textbf{Languages:} {HTML, CSS, JavaScript, TypeScript, SQL, Python, R, Bash, Markdown.} \\
        \textbf{Technologies:} {React, Next.js, Node.js, REST API, MySQL, NoSQL, Prisma, Redis, Firebase, Google Cloud Platform, Jupyter, Pandas, Git, GitHub, Docker.} \\
        \textbf{Courseworks:} {Object-Oriented Programming, Relational Database, Data Science, Data Structures, Algorithms, Network and 
Security, Linux Operating System.} \\
        \textbf{Certifications:} {Career Essentials in Administrative Assistance, Business Analysis, Data Analysis, Generative AI, Project Management, Software Development, System Administration by Microsoft and LinkedIn.} \\}}
    \end{itemize}


%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%
\section{References}
  \small{Available upon request.}
\end{document}
